---
title: "Strategy for GELASM SS2020"
subtitle: "An implementation in R Markdown"
author: "Peter von Rohr"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
```

# Introduction
```{r, echo=FALSE}
n_nr_courses <- 2
n_nr_weeks_per_semester <- 15
n_nr_weeks_taken <- 1 + 1 + 1
n_nr_weeks_lecture <- n_nr_weeks_per_semester - n_nr_weeks_taken
n_nr_weeks_per_course <- n_nr_weeks_lecture / n_nr_courses
```

The complete spring semester^[The semester starts on 2020-02-17 and ends on 2020-05-29.] lasts for `r n_nr_weeks_per_semester` weeks. The last two mondays are occupied by the test exam and the final exam and Easter Monday is a holiday. This leaves `r n_nr_weeks_lecture` for lectures. For each of the two courses ASM and GEL there are `r n_nr_weeks_per_course` weeks of lecture. 

In what follows, it is outlined what topics are tought and how the materials should be explained.


# Applied Statistical Methods in Animal Sciences^[ASM for short]


```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
if (!file.exists('skeleton.bib')) knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
