---
title: "Strategy for GELASM SS2020"
subtitle: "An implementation in R Markdown"
author: "Peter von Rohr"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
# initialise mendeley export obj
met <- rmddochelper::MendeleyExportToolR6$new()
# setting the current rmd-file
met$set_this_rmd_file(ps_this_rmd_file = ifelse(rstudioapi::isAvailable(),
                              rstudioapi::getActiveDocumentContext()$path,
                              rprojroot::thisfile()))
met$set_local_bib_file(ps_local_bib_file = 'skeleton.bib') 
```

# Introduction
```{r, echo=FALSE}
n_nr_courses <- 2
n_nr_weeks_per_semester <- 15
n_nr_weeks_taken <- 1 + 1 + 1
n_nr_weeks_lecture <- n_nr_weeks_per_semester - n_nr_weeks_taken
n_nr_weeks_per_course <- n_nr_weeks_lecture / n_nr_courses
```

The complete spring semester^[The semester starts on 2020-02-17 and ends on 2020-05-29.] lasts for `r n_nr_weeks_per_semester` weeks. The last two mondays are occupied by the test exam and the final exam and Easter Monday is a holiday. This leaves `r n_nr_weeks_lecture` for lectures. For each of the two courses ASM and GEL there are `r n_nr_weeks_per_course` weeks of lecture. 

In what follows, it is outlined what topics are tought and how the materials should be explained.


# Applied Statistical Methods in Animal Sciences^[ASM for short]
The title of this course is very broad and it leaves a lot of room for potential topics to be covered. The problem is with only `r n_nr_weeks_per_course` weeks, the number of lecture hours is small. There are two potential strategies that can be used to cope with the previously mentioned problem. 

1. We can either cover many different topics, but each topic is only treated very superficially.
2. We have to make some choices on the topics covered and leave out all the other topics. 

Both strategies have their pros and cons. In previous years, the second strategy was favored and only a selection of topics was covered. 


## Potential Topics
The set of potential topics is chosen from `r met$add('Essl1987')`. Those are^[The titles are translated in an ad hoc way from German into English]

1. Basic Terminology of Statistics
2. Probability Theory
3. Elementary Statistical Measures
4. Probability Distributions
5. Hypothesis-Testing
6. Multiple Coparisons of Means
7. Introduction into Matrix Computation
8. Basics of Parameter Estimation
9. Measures of Dependencies Between Traits
10. Multiple and Nonlinear Regression
11. Estimation of Fixed Effects
12. Prediction of Random Effects (BLUP)
13. Estimation of Variance- and Covariance Components
14. Non-parametric Applications
15. Experimental Design


## Choice of Topics
Chapters 7 and 8 can be taken as pre-requisites. The pre-requisites are included in the course notes, but not discussed in the course. Chapters 10 to 13 can be used as material in the course. The course notes start with a preface


## Preface


## Prerequisites


## Material





```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
if (!file.exists('skeleton.bib')) knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
