---
title: "Generate Multiple Linear Regression"
output:
  html_document:
    df_print: paged
date: '2020-02-24'
---

# Disclaimer
The original `bw-bc` regression data is augmented by two more predictor variables `BCS` and `HEI`. 


# Original Data
The original `bw-bc` data is read

```{r}
s_data_root_online <- "https://charlotte-ngs.github.io/GELASMSS2020"
s_data_root_local <- here::here() 
s_data_dir <- "ex/w03/bw_bc_reg.csv"
### # define data path depending on whether we are online or not
b_online <- FALSE
if (b_online){
  s_data_root <- s_data_root_online
} else {
  s_data_root <- s_data_root_local
}
s_data_path <- file.path(s_data_root, s_data_dir)
### # read data from s_data_path
tbl_reg <- readr::read_csv(file = s_data_path)
knitr::kable(tbl_reg,
             booktabs = TRUE,
             longtable = TRUE,
             caption = "Dataset for Regression of Body Weight on Breast Circumference for ten Animals")
```


# Extended Data
The existing data on body weight and breast circumference is extended by two more predictor variables. Both predictors are generated randomly. 

```{r}
set.seed(151413)
nobs <- nrow(tbl_reg)
l_bcs_par <- list(mean = 5, sd = 1.2)
l_hei_par <- list(mean = 150, sd = 13.5)
tbl_mult_reg <- tibble::add_column(tbl_reg, 
                                   BCS = round(rnorm(n = nobs, mean = l_bcs_par$mean, sd = l_bcs_par$sd), digits = 1),
                                   HEI = round(rnorm(n = nobs, mean = l_hei_par$mean, sd = l_hei_par$sd), digits = 0))
knitr::kable(tbl_mult_reg,
             booktabs = TRUE,
             longtable = TRUE,
             caption = "Dataset for Multiple Linear Regression of Body Weight")

```


# Writing Data To File
To make the extended data available for the exercise, we have to write it to a file.

```{r}
s_mult_data_file <- "ex/w03/bw_mult_reg.csv"
s_mult_data_path <- file.path(s_data_root, s_mult_data_file)
readr::write_csv(tbl_mult_reg, path = s_mult_data_path)
```


# Multiple Linear Regression
A test run for the multiple linear regression is done here. 

```{r}
mult_reg_bw <- lm(`Body Weight` ~ `Breast Circumference` + BCS + HEI, data = tbl_mult_reg)
summary(mult_reg_bw)
```


# Model Selection
By looking at the results alone, it is not clear which model should be chosen. Let us have a look at the different model selection tools.

```{r}

```

